% The acknowledgements section is optional. It can cover at most two pages.
\acknowledge{
	% If don't have an acknowledgment, comment out or delete this whole file
	The path to completing this dissertation would not have been possible without the support and guidance of many friends, mentors, and family members.
	I am especially grateful to my advisor, Stephanie Majewski, for her guidance and support, and for pushing me to not give up when I easily could have.
	I would also like to thank my committee members Spencer Chang and David Strom for their valuable feedback and mentorship throughout this dissertation.\par
	I am extremely grateful for the support, friendship, and guidance of the many friends and colleagues within ATLAS.
	I thank Jochen Heinrich for the research guidance, scotch recommendations, and Star Trek watch parties.
	I also thank Dani Koeck for the valuable discussions and allowing me to give her a hard time.
	Federica Piazza deserves thanks for guiding me through the complexities and challenges of the dark photon search, and bringing it to a timely and successful conclusion.
	I thank my mentors from BNL, Haider Abidi, Liza Brost, and Michael Begel, for believing in me and their invaluable advice.\par
	From the University of Oregon, I am grateful to Claire Staley and Anne McGinley for their support.
	I also thank my graduate student colleagues for their friendship and support during classes.\par
	To my closest friend, Michael Schmidt, thank you for your unwavering support and friendship, especially when times were challenging.
	To Gideon, my son, thank you for reminding me daily why I did this.
	Finally, I would like to thank my family for their love, sacrifice, and support to make this dissertation possible.

}

