This thesis describes two searches for new physics with the ATLAS detector at the LHC, with the focus of discovering or excluding dark matter signals.
The search for dark matter and BSM physics will continue to be a major focus of the ATLAS physics program in the coming years. 
By setting new and competitive limits on the production of dark mesons and dark photons, the BSM phase space is further constrained, and the results of these searches will be used to guide future searches for dark matter at the LHC and beyond.
% summarize dark meson findings here
Though no excess above the SM was observed in the Run 2 dark meson search, the strongest limits to date are obtained from the one-lepton channel.
For SU(2)$_L$ signals with $m_{\pi_D}/m_{\rho_D} = .45$, dark pions with masses below 940 GeV are excluded at 95\% CL, while for $m_{\pi_D}/m_{\rho_D} = .25$, the exclusion extends up to 740 GeV.
The dark meson results remain the first and most stringent limits on this type of model, extending the exclusion reach significannly compared to previous re-interpretations of LHC searches for similar signatures.
A Run 3 analysis has the potential to extend the exclusion reach with a dataset that is over twice as large as the Run 2 dataset.
With the large-R jet identification in the gFEX, the all-hadronic channel might be able to use direct triggering on boosted topologies, and lower the large $H_T$ requirement that cut out a siginificant fraction of the signal in the Run 2 analysis.
With generic multi-jet events being filtered more efficiently combined with a larger dataset, a revised all-hadronic channel may be able to reach sensitivities comparable to the one-lepton channel.

% summarize dark photon findings here

% summarize upgrade work + HL-LHC and future prospects here

